---
title: "Discussion 2"
author: "Ivan Ao"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Create a logical vector of length 6.  Set the first, fourth, and fifth elements to be TRUE and let the of the elements be FALSE. Call it `logi_vec`.
```{r}
logi_vec <- c(T, F, F, T, T, F)
logi_vec
```


2) Use the `as.double()` function to transform `logi_vec` into a double vector called `dbl_vec`. 
```{r}
dbl_vec <- as.double(logi_vec)
dbl_vec
```


3) Comment on what you noticed about this conversion in the previous prompt. 
It convert True to 1 and False to 0.

4) Check if each element of `logi_vec` is (strictly) less than 1. Do the same thing with `dbl_vec`. 
```{r}
logi_vec < 1
dbl_vec < 1
```


5) Write the the Pythagorean Theorem using markdown/latex math formula syntax. 

$a^2 + b^2 = c^2$

6) Write Newton's law of universal gravitation (on Elearn) using markdown/latex math formula syntax. 

$F = G \frac{m_{1}m_{2}}{r^2}$

