---
title: "Discussion 4"
author: "Ivan Ao"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1) There is a built-in data set called  `ChickWeight`. Load this data set into your environment. Open up the help file for this data set.  What does the "Description" in the help file say.
```{r}
CWeight <- ChickWeight
head(CWeight)
```
The ChickWeight data frame has 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks.


2) Determine the (arithmetic) mean of weights at `Time = 0`. 
```{r}
mean(CWeight$weight[CWeight$Time == 0])
```

3) Notice that there are 50 different chicks in the study, and the `Chick` column is an ordered factor with a non-obvious ordering structure.  Look at the help file to determine how the ordering was done for this factor column. \
Chick is an ordered factor with levels 18 < ... < 48 giving a unique identifier for the chick. The ordering of the levels groups chicks on the same diet together and orders them according to their final weight (lightest to heaviest) within diet.


4) Create a function that converts Celsius to Fahrenheit. 
```{r}
CToF <- function(C)
{
  return (C*1.8+32)
}
```

5) Try the temperatures 0, 32, 22.2, 37 for your function in Q4 and output the results. 
```{r}
CToF(0)
CToF(32)
CToF(22.2)
CToF(37)
```

6) Create a new data frame called `ChickWeight2` that contains all the chicks with weight greater than 200, and only contains the columns `weight` and `Time`. 
```{r}
ChickWeight2 <- data.frame(Weight = ChickWeight$weight[ChickWeight$weight > 200], Time = ChickWeight$Time[ChickWeight$weight > 200])
head(ChickWeight2)
```

