---
title: "Discussion 1"
author: "Ivan Ao"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Create a numeric object called `number` with a number of your choice. 
```{r}
number <- 1
number
```

2) Use a logical operator to check if `number` is less than 62. 
```{r}
number < 62
```

3) Create a numeric vector called `v` with the following elements: 5, 2, $\pi$, 8, 4.3, $e^3$
```{r}
v <- c(5, 2, pi, 8, 4.3, exp(3))
v
```


4) Use arithmetic operators to find the area of a sphere that has a radius of `number`. 
```{r}
pi * number^2
```


5) Use operators to create a vector of TRUE/FALSE values that correspond to the components of vector `v` that are between 2 and 4. 
```{r}
#bool <- c()
#for(x in v)
#{
#  bool <- c(bool, x < 4 & x > 2)
#}
#bool
(v < 4) & (v > 2)
```


6) Describe two different types of operators in your own words. 

%% reminder operator, for example a %% b = c, c will be the reminder after a / b
& and operator, for example a & b mean a and b must be both true if the output is true.

**Please fill out the following survey**: https://forms.gle/gQwp9dw1dRLXj9Jv9
