---
title: "Discussion 5"
author: "Ivan Ao"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1) Create a function check if an inputted temperature (`temp`) is extreme.  You can assume the temperature is in Fahrenheit units. Return a character vector of length one called `status` which indicates if the inputted `temp` is "boiling", "freezing", or "good". Check the temperatures 220, 101, 40, -15. (2 points)
```{r}
checkTemp <- function(temp)
{
  if(temp >= 212)
  {
    return(c("boiling"))
  }
  else if(temp >32)
  {    
    return(c("good"))
  }
  else
  {
    return(c("freezing"))
  }
  return(NA)
}
sapply(c(220,101,40,-15), checkTemp)
```




2) Use `sapply()` to check the following vector of temperatures for the Q1.  (1 point)

```{r}
F_temp <- c(23, 41, 50, 26.6,  42.8, 104.0,
            122.0,  78.8,  73.4,  59.0, 114.8,
            -19.4,  71.6,  96.8,  277.0,  -17.6,  46.4,  59.0, 
            51.8,  60.8,  64.4,  35.6,  289.6)
sapply(F_temp,checkTemp)

```


3) Create a function called `extreme.temp()` that has two arguments.  Let the first argument be named `IsCelsius`, and the second argument called `temp`. If `IsCelsisus=TRUE` then the `temp` is in Celsius units, and if `FALSE` then `temp` is in Fahrenheit units. In this function check if the inputted temperature is extreme.  Return a single character element called `status` which indicates if the inputted `temp` is "boiling", "freezing", or "good". You may use/call functions created in last weeks assignment, use the function above, or create any supporting functions that you need.  Check the temperatures 20C, 10F, and 150C. (2 points)
```{r}
extreme.temp <- function(IsCelsius,temp)
{
  if(IsCelsius)
  {
    if(temp >= 100)
    {
      return(c("boiling"))
    }
    else if(temp > 0)
    {
      return(c("good"))
    }
    else
    {
      return(c("freezing"))
    }
    return(NA)
  }
  else
  {
    return(checkTemp(temp))
  }
}
mapply(extreme.temp, c(T,F,T), c(20,10,150))
```


4) Download the data set `temperature_data.csv` on Elearn. The contains (pretend) experiment results collected by two researchers who used different units. Use `mapply()` to check if the temperatures are "boiling", "freezing", or "good". Display the first 15 values. (1 point)
```{r}
tempData <- read.csv("./temperature_data.csv")
mapply(extreme.temp,tempData$Celsius,tempData$Temperature)[1:15]

```






