---
title: "Homework 5(part 2)"
author: "haoyi Ao"
date: "2023-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(heatmap3)
```
## Random data
```{r}
data <- matrix(c(1,2,3,4,5,6,7,8,9,0,1,2,3,4,5,6,7,8,9,0,1,2,3,4,5,6,7,8,9,0,1,2,3,2,4,1), 
               nrow = 6, ncol = 6)
data
```


## Default graph
\
This give you the graph with all the default function.
```{r}
heatmap(data) 
```

# Function 1
The symm function can only be true when x is a square matrix. that means nrow = ncol. This will transpose the matrix. That mean column became row, and row became column.
```{r}
heatmap(data, symm = T)
```

# Function 2
The Rowv arguments determines how the row should be ordered by given a vector to order the row.
```{r}
heatmap(data, Rowv = c(10,9,8,7,6,5,4,3,2,1,0))
```

# Function 3
The Colv argument act the same as the Rowv. You can use Colv = "Rowv" only when row number is equal to col number to make sure the order in row and col are the same.
```{r}
heatmap(data, Rowv = c(10,9,8,7,6,5,4,3,2,1,0), Colv = "Rowv")
```

